### 2024-07-12 analysis/preprocessing.qmd
preprocessing updates

print(paste("We have", nrow(metaMER_results), "observations"))

print(paste("We have", length(unique(metaMER_results$citekey)), "studies"))

print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])), "are regression studies"))

print(paste("Where", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))
# note that we have some classification studies that also do regression and vice versa?
# THIS IS CORRECT:
# [1] "We have 1192 observations"
# [1] "We have 37 studies"
# [1] "Where 25 are regression studies"
# [1] "Where 12 are classification studies"

@@

R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2')) #  
R_studies$statistic
dim(R_studies)

@@

dim(R_studies)
R_studies$values[R_studies$measure=='R2']<-sqrt(R_studies$values[R_studies$measure=='R2']) # recode R2 into r
R_studies$values[R_studies$measure=='r2']<-sqrt(R_studies$values[R_studies$measure=='r2']) # recode R2 into r

@@

@@

# Deal with four studies involving multiple datasets: 
R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 744, soundtracks: 360, chinese: 500 "] <- 938 # resolved from the paper
R_studies$stimulus_n[R_studies$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372 # resolved
R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40 # decided to take this from validation
# REDO with a clearer function
eliminate <- str_detect(R_studies$unique_id,"hu2017cr") & !str_detect(R_studies$unique_id,"all")
R_studies <- R_studies[!eliminate,]
R_studies$stimulus_n[R_studies$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 60+818+1608 #
R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)

@@

g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
  scale_color_manual(values = c('black','white'))+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

@@

```{r}
R_studies$feature_n==" 15; 23 in table, but 15 reported "

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 1000),
                                      labels = c("Feature n < 18","Feature n > 18 & < 260","Feature n > 260"))
table(R_studies$feature_n_complexity)
```

@@

```{r}
tmp <- drop_na(R_studies)
library(ggdist)

@@

```
## Homogenise the stimulus N

@@

g1<-ggplot(C_studies,aes(x=values,fill=citekey,color=dimension))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

@@

- [ ] Ask Cameron whether it is OK to treat dimension contents as they are all classification studies (the exceptions are `av` and `valence` and `arousal`).

@@

```{r}
table(C_studies$feature_n)
C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')]<-548 
C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')]<-548 
C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
table(C_studies$feature_n)

C_studies$feature_n<-as.numeric(C_studies$feature_n)

>>>>

cat(paste("We have", nrow(metaMER_results), "observations"))

cat(paste("\nWe have", length(unique(metaMER_results$citekey)), "studies"))

cat(paste("\nWhere", length(unique(metaMER_results$citekey[metaMER_results$model_category=='regression'])), "are regression studies"))

cat(paste("\nWhere", length(unique(metaMER_results$citekey[metaMER_results$model_category=='classification'])), "are classification studies"))
# note that we have some classification studies that also do regression and vice versa?
# THIS IS CORRECT (updated 12 July 2024):
# [1] "We have 1238 observations"
# [1] "We have 37 studies"
# [1] "Where 23 are regression studies"
# [1] "Where 14 are classification studies"

# Add a check for these properties ToDo

@@

R_studies <- dplyr::filter(metaMER_results, measure %in% c('r','ccc','pcc','cc','r2','R2')) #

@@

R_studies$values[R_studies$measure=='R2']<-sqrt(R_studies$values[R_studies$measure=='R2']) # recode R2 into r
R_studies$values[R_studies$measure=='r2']<-sqrt(R_studies$values[R_studies$measure=='r2']) # recode R2 into r

@@

#table(R_studies$stimulus_n)

# Deal with four studies involving multiple datasets:

R_studies$stimulus_n[R_studies$stimulus_n==" emoMusic: 744, soundtracks: 360, chinese: 500 "] <- 938 # resolved from the paper
R_studies$stimulus_n[R_studies$stimulus_n==" 2372 (subset of PSIC3839, total n: 3839)    "] <- 2372 # resolved
R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 20; study 2: 40) % three outliers  "] <- 40 # decided to take this from validation
R_studies$stimulus_n[R_studies$stimulus_n==" study 1: 100; study 2: 20"] <- 20 #

R_studies$stimulus_n[R_studies$stimulus_n==" DEAM: 744, PMEmo: 206  "] <- 744 # we have encoded this based on stronger results on DEAM compared to PMEmo.

R_studies$stimulus_n[R_studies$stimulus_n==" NTUMIR: 60, MediaEval2013: 744  "] <- 60 # we have encoded this based on stronger results on NTUMIR compared to MediaEval

R_studies$stimulus_n[R_studies$stimulus_n==" 1020; MediaEval2014: 1000: music perception database 1: 6, music perception database 2: 9, music perception database 3: 8, music perception database 4: 7   "] <- 1020

# REDO with a clearer function
eliminate <- str_detect(R_studies$unique_id,"hu2017cr") & !str_detect(R_studies$unique_id,"all")
R_studies <- R_studies[!eliminate,]
R_studies$stimulus_n[R_studies$stimulus_n==" MER60: 60, CH818: 818, AMG1608: 1608  "] <- 60+818+1608 #

@@

R_studies$stimulus_n <- as.numeric(R_studies$stimulus_n)

@@

g1<-ggplot(R_studies,aes(x=values,fill=citekey,color=dimension))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
#  scale_color_manual(values = c('black','white'))+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

@@

@@

# Assign
R_studies$feature_n_complexity <- cut(R_studies$feature_n,
                                      breaks = c(0,
                                                 as.numeric(quantile(R_studies$feature_n,c(0.333),na.rm = T)),
                                                 as.numeric(quantile(R_studies$feature_n,c(0.666),na.rm = T)),
                                                 1000),
                                      labels = c("Feature n < 130","Feature n > 130 & < 653","Feature n > 653"))
table(R_studies$feature_n_complexity)
```

@@

```{r}
#tmp <- drop_na(R_studies)
tmp <- R_studies[!is.na(R_studies$values),]

library(ggdist)

@@

```
#### Get the number of categories in the classification task

```{r}
tmp <- metaMER_results
tmp2 <- tmp[which(tmp$statistic=='n'),]
no_of_classes <- summarise(group_by(tmp2,citekey),first(values))
print(no_of_classes)
rm(tmp,tmp2)
```

## Homogenise the stimulus N

@@

g1<-ggplot(C_studies,aes(x=values,fill=citekey))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

@@

@@

```{r}
table(C_studies$feature_n)
C_studies$feature_n[str_detect(C_studies$feature_n,'eight different ')]<-600 # arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'126, retained 97')]<-126 
C_studies$feature_n[str_detect(C_studies$feature_n,'1702; best model uses 100 after reduction')]<-1702 #  arbitrary!
C_studies$feature_n[str_detect(C_studies$feature_n,'548; after reduction, ')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'548 dimensions')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'548. Post-reduction')] <- 548 
C_studies$feature_n[str_detect(C_studies$feature_n,'8; 3 after')]<-8 
C_studies$feature_n[str_detect(C_studies$feature_n,'between 9 and 10')]<-10 
C_studies$feature_n[str_detect(C_studies$feature_n,'summarize feature')]<-600 # arbitrary
table(C_studies$feature_n)

C_studies$feature_n <- as.numeric(C_studies$feature_n)
